Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
put supplementary results in appendix

% Metrics : ROC AUC and AUPRC
In supervised learning term, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not E, \forall i \in V$) and some inference methods could spuriously
leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson correlation,
we set those elements to the minimum of $\hat{A}$ prior evaluating those
algorithms.

@@

\begin{table}[H]
\centering
\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

@@

>>>>

% Metrics : ROC AUC and AUPRC
In supervised learning term, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
spuriously leave maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
those algorithms.

@@

@@

\appendix

\section{Supplementary results}

\begin{table}[htbp]
\centering
\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htbp]
\centering
\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
\bottomrule
\end{tabular}
\end{table}
